Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-14 paper/ms.tex
Added more references

There are three primary applications we envision for the \celerite\ formalism: 1).\ modeling
the variability of an astrophysical system to infer it properties; 2).\
accounting for astrophysical variability as a source of noise when trying to detect
additional phenomena; 3).\ interpolating or extrapolating variability to future or missing
times.  Some examples of the first are determining the characteristic
variability timescale of a quasar, measuring the asteroseismic variation of a star,
or detection of quasi-periodic variability in a high-energy source.  Examples of the
second are detecting transiting exoplanets and correcting for stellar activity in
radial velocity measurements. Examples of the third are measuring time delays in
multiply-imaged gravitationally lensed sources and reverberation mapping of AGN.

@@

>>>>

There are three primary applications we envision for the \celerite\ formalism: 1).\ modeling
the variability of an astrophysical system to infer it properties; 2).\
accounting for astrophysical variability as a source of noise when trying to detect
additional phenomena; 3).\ interpolating or extrapolating variability to future or missing
times.  Some examples of the first are determining the characteristic
variability timescale of a quasar \citep{Kelly:2014}, measuring the asteroseismic variation of a star,
or detection of quasi-periodic variability in a high-energy source \citep{McAllister2016}.  
Examples of the
second are detecting transiting exoplanets and correcting for stellar activity in
radial velocity measurements \citep{Haywood2014,Rajpaul2015}. Examples of the third are 
measuring time delays in
multiply-imaged gravitationally lensed sources and reverberation mapping of AGN.

@@

In the future we hope to expand the \celerite\ technique to multi-dimensional
datasets.  The formalism presented could, for example, be used to model
the covariance between multiple measured quantities, such as in regression of photometric
time series versus astrometric precision when correcting for systematic errors
due to detector sensitivity variations \citep{Aigrain2016}, or in correcting
radial velocity datasets for stellar activity \citep{Haywood2014,Rajpaul2017}.
